\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Dino-Dodger}

\author{Team 39, S.R.A Squad
		\\ Shrey Mittal, mittas1
		\\ Razan Abujarad, abujarar
		\\ Zhiwen Yang, yangz18
}

\date{September 22, 2017}

%%\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 21, 2017 & Shrey Mittal & Problem Statement\\
September 21, 2017 & Razan Abujarad & Context of Problem\\
September 21, 2017 & Zhiwen Yang & Importance of Problem\\
December 4, 2017 & Razan Abujarad & Macid Correction\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{Problem Statement}
When taking a small break from work or simply seeking a source of simple entertainment for a short time period, people look for simple games to play on their PC or mobile devices because such games are easily available for free download and little action is required for the game to function and fulfill the entertainment need of the user. The goal of this project is to design a simple two-dimensional PC game for a single player, where the player controls a character that is continuously running in one direction and encountering various obstacles that must be overcome in order to score points, with the objective of the game to score as high as possible as the game progressively becomes more difficult.

\section{Importance of Problem}
In the present, more people are occupied with school and work, reducing the amount of leisure time. In other cases people simply look for sources of simple entertainment. It is also a fact that more people today have mobile devices and laptop PCs. In order to fulfill their entertainment needs in a simple and effective way, people play simple games that are easily available on app stores or webapp games using the Internet. Such games include \textit{Flappy Bird}, a simple and addictive game. This project is therefore important as it aims to fulfill this popular need of satisfying the entertainment needs of people that demand simplicity and easy accessiblity.

\section{Context of Problem}
This project is based on \textit{T-Rex Runner}, an open-source game developed by Chromium. This single user game consists of a small two-dimensional pixelated dinosaur running in one direction. Obstacles like cacti and birds flying at ground-level and sky-level must be overcome by pressing the spacebar to allow the dinosaur to jump when appropriate. Dino-Dodger is intended to be a redevelopment of this game.
~\newline
\subsection*{Stakeholders}
The stakeholders of the game are mainly the developers of the software and the single user interacting with the software when playing. Users may belong to any age group due to the simplicity of the game. 
\subsection*{Environment}
The environment of the existing game consists of a simple HTML page with minimal CSS styling. The HTML page containing the game is automatically displayed on the Google Chrome web browser on any PC or any mobile device as an error page whenever a website is unable to load or if there is an interruption in the Internet connection. 

%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}